Parallelization of Fast $\ell_1$-Minimization for Face Recognition

### 2011-03-08 paper/main.tex
Pretty much rewrote experiments section

In this section, we benchmark the performance of our algorithm on CPU and GPU platforms. 
In order to show how our $\ell_1$ minimization algorithms scale with problem size,
we will begin with benchmarks on synthetic data.  We will then progress to demonstrating 
the speed of our implementations as applied to the face recognition problem.

@@

The first experiment is designed to compare the two implementations of PALM
that solve a single large instance of the $\ell_1$-minimization problem (Algorithm \eqref{alg:alm}) by
comparing the amount of time to solve a problem given a generic random matrix $A$ and a random sparse
vector $\xx_0$.  
The measurement $d \times n$ matrix $A$ was generated as a random Gaussian matrix, with each entry
randomly generated from the standard normal and normalized with unit norm.  The ratio of $d:n$ varied from
$10:1$ to $10:5$ with the dimension of $d$ of matrix $A$ varying from 500 to 8000.
The ground truth signals, $\xx_0$ had a sparsity rate of 0.1 with elements generated using the standard normal and normalized with unit norm.
Because the ground truth signal $\xx_0$ is known, the algorithm terminates
when $norm(\bx-\bx_0) < tolerance$.
The measurement vector was generated with the equation $\y_0 = A \x_0$.   
We also varied the different inner and outer tolerance levels from 1e-2 to 1e-5.
We averaged the the time taken for the ALM algorithm to solve 10 instances of a problem.

%The x set of experiments will compare the CPU and GPU versions of the entire pipeline, 
%which includes the alignment and recognition stage.

The second experiment is to compare the amount of time to solve the face alignment
stage for each implementation.  Because the alignment stage is not affected by the resolution of the image,
we fix the resolution at 60x80.

Since we use a reduced training set for the recognition stage, our third experiment was to 
find the relationship between the probability that the true subject is in the training set vs the
 number of users in the reduced training set and the speed of the recognition stage w.r.t.
 the number of subjects in the training set.

The fourth experiment is to compare accuracy rate of the face recognition algorithm at different
image resolutions.  We fixed the number of users to be $enter here$ which was shown in figure  $enter here$  have 95\% probability
to have the true user in the training set, inner loop tolerance to 1e-2 and outer loop tolerance to 1e-3.

@@

\subsection{Simulation}
\label{sec:simulation}

We plot the most significant results of the simulation benchmark below.  The x-axis represents the size of the 
$A$ matrix and the y-axis represents the average amount of time it to complete a single problem instance.

\begin{figure}[sim_plot]
\begin{center}
      \includegraphics{../results/random_data/time_vs_matrix_size_constant_tol}
\end{center}
\caption{Speed vs Dimensions of A.  Outer loop tolerance = 0.1.  Inner loop tolerance = $10^{-5}$}
\end{figure}

The observations of this experiment are summarized below:
1.  With similar accuracy rates, the GPU implementation runs faster than the CPU at the crossover points 
noted on the plots.
2.  From the results, it was seen that tolerances...

\subsection{Face Alignment Benchmark}
\label{sec:alignment_benchmark}

\subsection{Face Recognition Benchmarks}
\label{sec:recognition_benchmark}

\subsection{Face Recognition Benchmark}
\label{sec:pipeline_benchmark}

>>>>

In this section, we benchmark the performance of our algorithm on CPU and GPU
platforms.  In order to show how our $\ell_1$ minimization algorithms scale
with problem size, in Section \ref{sec:simulation} we will begin with
benchmarks on synthetic data.  We will then progress in Sections
\ref{sec:alignment_benchmark} and \ref{sec:recognition_benchmark} to
demonstrating the speed of our implementations as applied to the alignment and
recognition stages of the face recognition problem.

@@

\subsection{Simulations on Random Data}
\label{sec:simulation}

The first experiment compares the performance of our two proposed implementations of 
the general $\ell_1$-minimization problem (Algorithm \eqref{alg:alm}) by
comparing the amount of time to solve a problem given a generic random matrix $A$ and a random sparse
vector $\xx_0$.  
The measurement $d \times n$ matrix $A$ was generated as a random Gaussian matrix, with each entry
randomly generated from the standard normal and normalized with unit norm.  The ratio of $d:n$ varied from
$10:1$ to $10:5$ with the dimension of $d$ of matrix $A$ varying from 500 to 8000.
The ground truth signals, $\xx_0$ had a sparsity rate of 0.1 with elements generated using the standard normal and normalized with unit norm.
Because the ground truth signal $\xx_0$ is known, the algorithm terminates
when $norm(\bx-\bx_0) < tolerance$.
The measurement vector was generated with the equation $\y_0 = A \x_0$.   
%We also varied the different inner and outer tolerance levels from 1e-2 to 1e-5.
We averaged the time taken for the ALM algorithm to solve 10 instances of a problem.

The results of this benchmark can be found in Figure \ref{fig:random_data}.
The x-axis represents the size of the $A$ matrix and the y-axis represents the
average amount of time it to complete a single problem instance.  A can be seen
in Figure \ref{fig:random_data}, the GPU implementation tends to be faster than
the CPU implementation at solving a single large problem, whereas the the CPU
implementation is faster at solving a single small problem.  
\begin{figure}
\label{fig:random_data}
\begin{center}
      \includegraphics{../results/random_data/time_vs_matrix_size_constant_tol}
\end{center}
\caption{Speed vs Dimensions of A.  Outer loop tolerance = 0.1.  Inner loop tolerance = $10^{-5}$}
\end{figure}

\subsection{Face Alignment Stage Benchmark} \label{sec:alignment_benchmark}
This section presents benchmarks of our CPU and GPU implementations of the
alignment stage of the face recognition pipeline described in Algorithm
\ref{alg:iterative_alignment}.  The iterative alignment seeks a similarity
transformation between the coordinate frame of the "camera" resolution test
image and the coordinate frame of the "canonical" resolution images which the
images are compared.  We use a $64$ pixel wide square window in the canonical
frame.  The training images are aligned by manually clicking the two outer eye
corners in the camera frame, and then warping the images via a similarity
transformation such that the eye corners lie at a pair of canonical eye
locations in the canonical frame.  The canonical eye corners are chosen such
that for well aligned images, the canonical window contains exclusively pixels
from the subject's face.

For experiments on face data we use subsets of the CMU Multi-PIE Face Database.
For gallery images we use frontal images from session 1, which contains 20
images per user taken under different illuminations. For test images we use
images from session 2.

In Figure \ref{fig:alignment_stage_runtime} we report the time it takes
to align a single test image against each of the users in the gallery.
We vary the size of the gallery to show how implementation scales in the
number of gallery users.
\begin{figure}
\centering
\includegraphics[width=3.5in]{figures/alignment_stage_runtime.pdf}
\caption{Alignment Stage Time vs. Size of Training Database}
\label{fig:alignment_stage_runtime}
\end{figure}

\subsection{Face Recognition Stage Benchmarks}
\label{sec:recognition_benchmark}
Since we use a reduced training set for the recognition stage, our third
experiment was to find the relationship between the probability that the true
subject is in the training set vs the number of users in the reduced training
set and the speed of the recognition stage w.r.t.  the number of subjects in
the training set.

\subsection{Face Recognition Benchmark}
\label{sec:pipeline_benchmark}
The fourth experiment compares the recognition rate of the face recognition algorithm at different
image resolutions.  We fixed the number of users to be $enter here$ which was shown in figure  $enter here$  have 95\% probability
to have the true user in the training set, inner loop tolerance to 1e-2 and outer loop tolerance to 1e-3.

@@
